---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `nurser`

<!-- badges: start -->
<!-- badges: end -->

An R package for streamlining the front end of the machine learning workflow.


### Summary  

---

Common to the front end of most machine learning pipelines is an exploratory data analysis (EDA) and feature preprocessing. EDA's facilitate a better understanding of the data being analyzed and allows for a targeted and more robust model development while feature imputation and preprocessing is a requirement for many machine learning alogirthms. `nurser` aims to streamline the front end of the machine learning pipeline by generating descriptive summary tables and figures, various feature imputation summaries, and automating preprocessing. Automated preprocessing detection has been implemented to minimize time and optimize the processing methods used. The functions in `nurser` were developed to provide useful and informative metrics that are applicable to a wide array of datasets.   

_`nurser` was developed as part of DSCI 524 of the MDS program at UBC._  


### Installation:

---

You can install the released version of nurser from CRAN with:

```
install.packages("nurser")
```

The development version can be downloaded from [GitHub](https://github.com/UBC-MDS/nurser) with: 

```
# install.packages("devtools")
devtools::install_github("UBC-MDS/nurser")
```

### Features

---

The package includes the following three functions:  

|Function|Input|Output|Description|
|--------|-----|------|-----------|
|`eda`|- a dataframe|- a list that contains histogram and summary statistics for each column|- Functionality for easy explanatory data analysis. |
|`impute_summary`|- a dataframe|- a list with summary statistics and outputs of different imputation methods|- Functionality for consolidating several imputation methods|
|`preproc`|- a tibble or dataframe|- a tibble with preprocessed features|- Functionality for automatic feature preprocessing detection and user defined feature preprocessing|  


### R Ecosystem  

---

`nurser` was developed to align with:  

- [tidyverse](https://www.tidyverse.org/) 

The `impute_summary` function leveraged the imputation  methods found in the following packages:  

- [Hmisc](https://cran.r-project.org/web/packages/Hmisc/index.html)    
- [mi](https://cran.r-project.org/web/packages/mi/index.html)    
- [mice](https://cran.r-project.org/web/packages/mice/index.html)   
- [missForest](https://cran.r-project.org/web/packages/missForest/index.html)  
 

However, the functions herein streamline and automate the front-end machine learning pipeline for use with any machine learning package.  


### Dependencies

--- 

- ggplot2=3.2.1

### Usage

---  

```{r example}
#library(nurser)
## basic example code
```

### Documentation

---

