---
title: "nurser-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nurser-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



# Introduction

The functions in `nurser` were developed to provide useful and informative front-end machine learning metrics that are applicable to a wide array of datasets. Currently `nurser` contains three functions, each of which are independent of one another. This vignette outlines how to use these functions on some real data.

---

```{r setup}
library(nurser)
library(magrittr)
```

# `eda`

The `eda()` function return a list that contains histogram and summary statistics for a given column. Let's see it in action! 

</br>

To view a histogram of a feature:

```{r include = FALSE, message = FALSE}
result <- eda(mtcars)
```
```{}
result <- eda(mtcars)
```
```{r eda1, message = FALSE}
hist_mpg <- result$histograms[[1]]
hist_mpg
```
</br>

Now let's see the summary statistics of this feature:  

```{r eda2}
stats_mpg = result$stats$mpg
stats_mpg
```

---

# `impute_summary`

Let's import some continuous data to work with,
```{r impute1}
iris_data <- iris[1:4]
```

and add some missing values, 

```{r impute2}
iris_missing <- 
  as.data.frame(lapply(iris_data, 
                       function(x) x[sample(c(TRUE, NA),
                                            size = length(x), 
                                            replace = TRUE,
                                            prob = c(0.75, 0.25))]))
```

Now, let's take a look at the data to in fact see if the missing values were generated and where they are:

```{r impute3}
iris_missing %>% head(10)
```

Great, we have some missing values to compute - let's call `impute_summary` to get some summary statistics and outputs from different methods.

```{r impute4, include = FALSE}
iris_imputed <- impute_summary(iris_missing)
```

```{}
iris_imputed <- impute_summary(iris_missing)
```

`impute_summary()` provides some useful summary statistics and also several imputed dataframes that can be accessed by the impute_summary object attributes. The imputed data frames provided include:

  - mean,   
  - median,   
  - max,   
  - min,  
  - random,  
  - multiple imputation,   
  - pmm, and  
  - random forest  

Let's first take a look at the summaries, which can be accessed using __`$nan_counts`__ (NA counts for each feature) and __`$nan_rowindex`__ (rows that contain NA values):

```{r impute5}
iris_imputed$nan_counts

iris_imputed$nan_rowindex %>% head(5)
```

</br>

Now, let's take a look at two of the imputed data frames, __`mean`__ and __`multiple imputation`__:

```{r impute6}
iris_imputed$hmisc_mean %>% head(10)

iris_imputed$mi_multimp %>% head(10)
```


---

# `preproc`

The `preproc()` function returns a tibble with preprocessed features. Simply call `preproc` on your data!

Let's first view our data before preprocessing:

```{r}
head(iris)
```

</br>

and now after calling `preproc`:  
```{r}
results = preproc(iris)
head(results)
```


---

